\showyourwork: a workflow for open source scientific articles

### 2022-09-21 src/tex/ms.tex
dynamic tables

% Define document class
\documentclass[modern]{aastex631}

@@

\begin{table}[p!]
    \begin{center}
        \begin{tabular}{@{}l|l@{}}
            \hline
            Name & Representation \\
            \hline
            \variable{output/kernels.tex}
        \end{tabular}
    \end{center}
    \caption{A table with programmatically-generated output. Reproduced from Table 1 in \citet{Aigrain2022}. \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
    \label{tab:variable}
\end{table}

>>>>

% Define document class
\documentclass{aastex631}

@@

\begin{table}
    \begin{center}
        \begin{tabular}{@{}l|l@{}}
            \hline
            Name & Representation \\
            \hline
            \variable{output/kernels.tex}
        \end{tabular}
    \end{center}
    \caption{The functional forms of various commonly used Gaussian process kernels; reproduced from Table~1 in \citet{Aigrain2022}.
    The contents of this table are programmatically generated; the kernels are defined as \texttt{sympy} expressions and rendered into \texttt{TeX} form in the script \texttt{src/scripts/kernels.py}.
    The autogenerated \texttt{GitHub} icon in the margin links to the rule in the \texttt{Snakefile} that runs that script.
    \xxx{@dfm: is it ok for us to reproduce this table of yours?}}
    \label{tab:variable}
\end{table}
